---
title: "How to make beautiful tables in R"
format: html
---
```{r}
library(tidyverse)
library(kableExtra)
```

```{r}
datapasta::df_paste()

whale_sightings <- data.frame(
  stringsAsFactors = FALSE,
              date = c("8/12/2014","8/13/2014",
                       "8/15/2014","8/16/2014","8/16/2014"),
              site = c("channel", "channel", "harbor", "channel", "channel"),
               spp = c("unknown", "gray", "gray", "humpback", "gray"),
            dist_m = c(400L, 200L, 60L, 300L, 150L),
          behavior = c("breach", "spout", "spout", "feeding", "feeding")
)
```

```{r}
#| echo:  false
whale_sightings %>% 
  kableExtra::kable( ##specify column names
    col.names = c("Date", "Site", "Species",
                                  "Distance (m)", "Behavior")) %>% 
  #table themes
  kableExtra::kable_classic() %>% 
  #individual aspects
  
  #edit look of columns
  column_spec(1, bold = TRUE, background = "yellow") %>% 
  
  column_spec(2, italic = TRUE, background = "orange") %>% 
  
  #Creates a header/s above the columns
  add_header_above(c(" " = 1, "One header" = 2, "Another header" = 2)) %>% 
  
  #creates a scroll box (for when tables have a lot of information)
  scroll_box(height = "100px", width = "700px")
```


whale_sightings %>% 
  kableExtra::kable( ##specify column names
    col.names = c("Date", "Site", "Species",
                                  "Distance (m)", "Behavior")) %>% 
  #table themes
  kableExtra::kable_classic() %>% 
  #individual aspects
  
  #edit look of columns
  column_spec(1, bold = TRUE, background = "yellow") %>% 
  
  column_spec(2, italic = TRUE, background = "orange") %>% 
  
  #Creates a header/s above the columns
  add_header_above(c(" " = 1, "One header" = 2, "Another header" = 2)) %>% 
  
  #creates a scroll box (for when tables have a lot of information)
  scroll_box(height = "100px", width = "700px")